Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-10-10 paper/tex/analysis.tex
add sentence on implicit prior

The interpretation of the information $I_{H}$ is more subtle.
This investigation is built upon the knowledge that two codes taking the same approach, among choices of model fitting or machine learning, are nonetheless expected to yield different results even if they take the same external prior information $I_{D}$.
$I_{H}$ represents the projection of the code's architecture onto the estimated posteriors over redshift, specific to each code, and even the tunable parameters or random seeds of a specific run of a code with a random component.
We thus refer to $I_{H}$ as the \textit{implicit prior}, in contrast with the training set or template library provided to a given code explicitly by the researcher.

>>>>

The interpretation of the information $I_{H}$ is more subtle.
This investigation is built upon the knowledge that two codes taking the same approach, among choices of model fitting or machine learning, are nonetheless expected to yield different results even if they take the same external prior information $I_{D}$.
$I_{H}$ represents the projection of the code's architecture onto the estimated posteriors over redshift, specific to each code, and even the tunable parameters or random seeds of a specific run of a code with a random component.
We refer to $I_{H}$ as the \textit{implicit prior}, in contrast with the training set or template library provided to a given code explicitly by the researcher.  In simple terms, the implicit prior is the collection of the many different assumptions, coding choices, algorithm selections, and other implementation details that are specific to each code, the ensemble of which results in differing estimates of redshift when combined with the data and prior information in common to all codes.
